\newpage
\begin{section}
    {Code Testing}
    \begin{itemize}
        \item The ability to test your own code is integral to an understanding of data structures.
        \begin{itemize}
            \item Differentiating between requirements and design decisions you made.
            \item Coming up with test cases is one of the best ways to understand data structures more deeply.
            \begin{itemize}
                \item What cases will cause certain implementations to slow down?
                \item How long do I expect certain operations to take?
                \item What edge cases are there in the definition?
                \item Where else might I find bugs?
            \end{itemize}
        \end{itemize}
        \item In the real world, coding projects don’t come with their own tests.
        \begin{itemize}
            \item You have to write your own.
        \end{itemize}
        \item Learning to test your own code is integral to maturing as a computer scientist.
    \end{itemize}
    
    \begin{itemize}
        \item Types of Tests
        \begin{itemize}
            \item Black Box
            \begin{itemize}
                \item Behavior only - requirements
                \item From an outside point of view
                \item Does your code uphold its contracts with its users?
                \item Performance/efficiency
            \end{itemize}
            \item White Box
            \begin{itemize}
                \item Includes an understanding of the implementation
                \item Written by the author as they develop their code
                \item Break apart requirements into smaller steps
                \item "unit tests" break implementation into single assertions
            \end{itemize}
        \end{itemize}
    \end{itemize}
    
    \begin{itemize}
        \item What to Test?
        \begin{itemize}
            \item Expected behavior
            \begin{itemize}
                \item The main use case scenario
                \item Does your code do what it should given friendly conditions?
            \end{itemize}
            \item Forbidden Input
            \begin{itemize}
                \item What are all the ways the user can mess up?
            \end{itemize}
            \item Empty/Null
            \begin{itemize}
                \item Protect yourself!
                \item How do things get started?
                \item 0, -1, null, empty collections
            \end{itemize}
            \item Boundary/Edge Cases
            \begin{itemize}
                \item First items
                \item Last item
                \item Full collections (resizing)
            \end{itemize}
            \item Scale
            \begin{itemize}
                \item Is there a difference between 10, 100, 1000, 10000 items?
            \end{itemize}
        \end{itemize}
    \end{itemize}
\end{section}
