\newpage
\begin{question}
Show that a directed multigraph having no isolated vertices has an Euler circuit if and only if the graph is weakly connected and the in-degree and out-degree of each vertex are equal.
\end{question}

\par\noindent\rule{\textwidth}{0.5pt}

\subsubsection*{Solutions} Prove the following two statements:\bigskip

\noindent
($\leftarrow$) A directed multigraph having no isolated vertices has an Euler circuit, then the graph is weakly connected and the in-degree and out-degree of each vertex are equal.

\begin{itemize}
    \item Euler circuit visits every nodes, so the graph is weakly connected.
    \item The start and end node is equal, so the in-degree and out-degree of start(end) node is equal now. During the Euler circuit, we have to enter and exit the node, so the in-degree and out-degree of each node(contain start and end node) are equal.
\end{itemize}

\bigskip\noindent
($\rightarrow$) A directed multigraph is weakly connected and the in-degree and out-degree of each vertex are equal, then the graph has an Euler circuit.

\bigskip\noindent
We already know the theorem that a connected multigraph with a least two vertices has an Euler circuit if and only if each of its vertices has even degree (during class). A graph is weakly connected, so we can know that the every nodes are connected if we ignore the direction. Also, we know that the in-degree and out-degree of each vertex are equal, so every nodes have even degree. Therefore, the graph has an Euler circuit by theorem.
